---
title: "Studying GPS Spect"
author: "Naeem Khoshnevis"
date: "6/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this document we focus on effect of different parameters in generating synthetic data. 

## Load libraries

```{r}
library(ggplot2)
library(GPCERF)
```

## Overview 

The synthetic data is generated using `generate_synthetic_data.R` function. The function accepts the following input values. 

**`sample_size`**: Number of data samples.
**`outcome_sd`**: Standard deviation used to generate the outcome in the synthetic data set.
**`gps_spec`**: A numeric value (1-6) that indicates the GPS model used to generate the continuous exposure.
**`cova_spec`**: A numeric value (1-2) to modify the covariates.

## Example 

Let's say we want to generate a synthetic dataset with 1000 data samples. 

```{r, cache=TRUE}
data_1 <- generate_synthetic_data(sample_size = 1000,
                                  outcome_sd = 10,
                                  gps_spec = 1,
                                  cova_spec = 1)

summary(data_1)
```

Let's take a look at the overal data plots.

```{r, cache=TRUE}
plot(data_1)
```

cf1 ~ cf4 is generated using multivariate normal distribution. 



